\documentTitle{\myName}{
\href{tel: \tel}{
	\raisebox{-0.05\height} \faPhone\ \tel} ~ | ~
\href{mailto:\email}{
	\raisebox{-0.15\height} \faEnvelope\ \email} ~ | ~
\href{\linkedin}{
	\raisebox{-0.15\height} \faLinkedin\ \linkedin} ~ | ~
\href{\github}{
	\raisebox{-0.15\height} \faGithub\ \github }
}

\subsubsection*{Dear Rune:}

\paragraph{}
I'm delighted to write this letter to you. Since I learned about Ephort and was inspired by its website, I have been enthusiastic about applying for a position there to further my career and expand my knowledge.

\paragraph{}
From the content on Ephort's homepage, Ephort shows a friendly and enjoyable company culture between the lines. And display the purpose of delivering exceptional products to customers. Ephort's culture and environment are extremely attractive to developers. The name Kristian, the senior developer, is mentioned in many customer quotes, which impresses me.

\paragraph{}
Ephort always embraces new technology and devotes itself to improving and implementing it with innovation. As presenters, organizers, and participants engage in tech meetups (Laravel EU) and hold development days(hackathons), all those events interest me. Like Ephort, I'm especially interested in back-end development, although my main area is front-end development. I want to be part of this process and reach the team and personal goals with Ephort's culture and environment. 

\paragraph{}
Ephort's commitment to innovation and technology aligns perfectly with the skills and knowledge I have developed through my education and practical experience in software development.

\paragraph{}
My educational background at Business Academy Southwest gave me a comprehensive understanding of software development principles, including web development, software design, and DevOps. I strongly advocate for TDD and CI/CD, having implemented these practices comprehensively throughout my academic projects, utilizing tools like Jenkins and Docker. I am also passionate about modular design principles and clean code(especially the onion architecture and dependency injection), ensuring code is readable, reusable, and adaptable. 

\paragraph{}
After completing my education, I joined Bifrostconnect, where I had a chance to work on real projects and gain hands-on experience. I am improving user experience and efficiency in development with the new knowledge in React and Golang. My responsibilities bridged both front-end and back-end development, which fostered a well-rounded skill set. I developed and refined core features and collaborated with my team to contribute ideas and solutions. I initiated the creation of a code style guide and set up a testing framework for front-end development, enhancing code quality and maintainability. I contributed to the release process by drafting strategies based on our branching and environment setups. This experience enhanced my knowledge of the software development lifecycle and developed my skills in version control with Git and GitHub.

\paragraph{}
Based on my educational background and on-field experience, I can handle full-stack development across the entire software development lifecycle. I have an extensive vision of software construction to offer to Ephort's application development project. Specifically, I can explore the software development project on React/Angular projects corresponding with the JAVA/C\#/Golang-based server. I know how to design the database and implement specific usage. I can offer an effective distribution system to meet customer needs. I can also provide the branch strategy design and the CI/CD pipeline design to help implement the DevOps procedures successfully.

\paragraph{}
In my life, lift-circle learning and thinking keep a person's mind active. Organizing, analyzing, and optimizing improve everything. In my free time, I'm looking at technology that is outside my work scope, such as Vim, Vite, Latex, R, etc. I'm currently starting Vue.js.

\paragraph{}
I am also learning to play a skateboard sometimes. I loved to play basketball even though I'm not a taller guy. I did 5 km in the DHL race once this year. :D

\paragraph{}
I'm married and live in Odense SØ. We don't have a child, but we have a cat about the cat. (That is another lovely story. )

\paragraph{}
Thank you for your time to read this letter. We can have a face-to-face conversation if I get some attention from you. :D

\paragraph{}
{\hfill Sincerely,} \par
{\hfill Fei Gu} \par
{\hfill \today} \par
