\section{Experiences}

%% Bifrost Full-time
\headingBf{\large{BifrostConnect Aps.}}{Aug 2023 -- persent}
\headingIt{Junior Software Developer}{Københaven, Denmark}
\begin{resume_list}
\vspace{0.5em}
\itemTitle{\textbf{React web application}}
\item Participate with the team to develop and implement the new features included the UI/UX improvement.
\item Implement the ESLint/Prettier for the code style and auto-formatting.
\item Implement the unit test framework such as Jest and prepare for the continuing test implementation.
% \item Spearhead the components encapsulation and refactoring .
\vspace{0.5em}
\itemTitle{\textbf{Vanila JS web application}}
\item The multiple legacy issue analysis and the bug fix.
\item Participate in the new feature's design and development.
\item Participated in documenting the issues and the development log.
% \item Branch strategy design and release strategy design.
\vspace{0.5em}
\itemTitle{\textbf{Golang server}}
\item Web API design and the endpoint implementation using Gin framework.
\item Database API design and implement the query to operate the Database using GROM. 
\item Participated in the Go project OOP implementation and the software architecture.
\end{resume_list}

\vspace{1.5em}
%% Bulefin manager
\headingBf{\large{Bluefin Copenhagen ApS / Bluefin Sushi ApS}}{2018 -- 2022}
\headingIt{Restaurant manager}{Odense, Denmark}
\begin{resume_list}
\item Daily Operation design and implementation, hygiene check, regularly working process improvement.
\item Employee management such as designing working schedules and employee performance support.
% \item Calculating the storage, place an order for supply.
\item Customer service, customer issues resolve.
\end{resume_list}
% \headingIt{Sushi Chef}{Odense, Denmark}
% \begin{resume_list}
% \item Material preparation.
% \item Delivery the sushi product.
% \end{resume_list}

% %% 电话销售
% \headingBf{Bangson Global intellectual property Tianjin company}{Aug 2010 -- Aug 2011}
% \headingIt{Telephone sales and intellectual Property counselor}{Tianjin, China}
% \begin{resume_list}
% \item Cold call the potential customer to introduce the company's service.
% \item Offer the intellectual property service to the potential customer.
% \end{resume_list}

% %% 健康公司
% \headingBf{Tianjin Saiyuan Health company}{Aug 2009 -- Aug 2010}
% \headingIt{Market Regional Manager Assistant}{Tianjin, China}
% \begin{resume_list}
% \item Assistant the regional manager to design the market strategy.
% \item Contect the franchiser, offering the sales support and the product training.
% \item Coprate with franchiser to improve the sales performance.
% \end{resume_list}
