\section{Skills}

\begin{itemize}[leftmargin=1em, label={$\bullet$}]
    \item \textbf{Backend Development:}  
        \begin{itemize}
            \item \textbf{C\# / .NET / Entity Framework:} Building adaptable backend services with clean architecture.
            \item \textbf{Golang / GORM / GIN:} Creating simple, scalable backend services for microservices architecture.
            \item \textbf{Clean Architecture (Onion / Hexagonal):} Experience implementing scalable and maintainable architectures.
        \end{itemize}
    \item \textbf{Frontend Development:}  
        \begin{itemize}
            \item \textbf{HTML / CSS / SASS / Tailwindcss:} Strong foundation and adherence to best practices.
            \item \textbf{React / NextJS / Redux / React Router:} Designing user-friendly and dynamic UI components.
            \item \textbf{JavaScript / Node.js:} Experience with vanilla JavaScript in real-world projects.
            %   \item \textbf{Angular / RxJS:} Developing scalable front-end applications.
            \item \textbf{HOC / Functional Programming / OOP:} Practical understanding and application in real scenarios.
        \end{itemize}
    \item \textbf{Databases (MSSQL, MySQL, PostgreSQL, SQLite):} Designing, maintaining, and migrating databases.
    \item \textbf{API Development (RESTful API / GraphQL):} Selecting and implementing APIs based on project needs.
    \item \textbf{Git / GitHub:} Proficient in using Git CLI commands and managing repositories on GitHub.
    \item \textbf{Branching Strategy:} Designing and implementing strategies for different team sizes.
    \item \textbf{CI/CD (Jenkins, GitHub Actions):} Automating workflows and ensuring continuous integration/deployment.
    \item \textbf{Docker:} Building and deploying distributed systems and microservices.
    \item \textbf{Distributed Systems / Microservices:} Practical implementation in production environments.
    \item \textbf{IoT Communication (MQTT / WebRTC):} Implementing real-time communication for IoT devices.
\end{itemize}
